---
title: "Statistical Inference Assesment Part 1"
author: "Sergey Chigrinov"
date: "November 12, 2015"
output: pdf_document
---
The goal of the analysis is to demonstrate the Central Limit Theorem using the exponential distribution.
The distribution can be simulated in R with rexp(n, lambda). In our case, lambda = 0.2 and n=40. To better illustrate the concept we'll run 1000 simulations to generate datasets. While simulating, let's calculate the mean and variance.
```{r}
set.seed(1)
lambda<-0.2
n=40
n.simulations <- 1000
exp.data = NULL
exp.means <- NULL
for(i in 1:n.simulations) { 
    tmp <- rexp(n,lambda)
    exp.means <- c(exp.means, mean(tmp))
    exp.data <- cbind(exp.data, rexp(n,lambda))
}
```
While the theoretical value of the the mean equals 1/lambda, the mean of our simulated example stands pretty close
```{r}
#Mean
matrix(nrow = 2, data=c("Theoretical",1/lambda,"Simulated",round(mean(exp.means),3)))
```

The theoretical value of the standard deviation of the exponential distribution is also 1/lambda.
The variance of the sample mean equals (1/lambda)^2/n.
```{r}
#Variance
matrix(nrow = 2, data=c("Theoretical",round((1/lambda)^2/n,3),"Simulated",round(var(exp.means),3)))
```
From the histogramm we can see that distribution of the means is approximately normal.
```{r}
hist(exp.means,freq=FALSE)
abline(v=1/lambda, col="red")
curve(dnorm(x, mean=1/lambda, sd=1/lambda/sqrt(n)), add=TRUE, col="blue", lwd=2)
```

Based on the above analysis we can conclude that the mean value of the exponential distribution is subject to normal distribution, which confirms the Central Limit Theorem.
